On the analytic structure of the linear response susceptibility in open systems

### 2018-04-27 AnalyticStructure_main.tex
update

\section{Introduction}
The subject of the present investigation concerns with the study of isolated molecular-like systems subjected to a time-dependent perturbation. % in the linear response regime.
This problem can be tackled within the contest of the time-dependent density functional theory (TD-DFT) \cite{runge1984,onida2002}, that allows one to establish the time-dependent 
Kohn-Sham (KS) equations which determine the evolution of the one-particle properties of the system with respect to time.

>>>>

\section{Introduction}

The subject of the present investigation concerns with the study of isolated molecular-like systems subjected to a time-dependent perturbation. % in the linear response regime.
This problem can be tackled within the contest of the time-dependent density functional theory (TD-DFT) \cite{runge1984,onida2002}, that allows one to establish the time-dependent 
Kohn-Sham (KS) equations which determine the evolution of the one-particle properties of the system with respect to time.
